Wrinkling of a confined porous layer

### 2014-05-23 poster_Okinawa.tex
Poster pour Okinawa : change le titre, les auteurs et les logos

\usepackage{hyperref}
\hypersetup{%
	pdftitle={Wrinkling and yielding of protein gels},%the title
	pdfauthor={Mathieu Leocmach},%your name
}

@@

% This gives good title positioning for a portrait poster.
% Watch out for hyphenation in titles - LaTeX will do it
% but it looks awful.
\begin{textblock}{15}(0,0)
\centering
\Title{
Wrinkling and yielding of protein gels
}

\LHead{Mathieu Leocmach}\qquad\texttt{\color{Accent1}mathieu.leocmach@ens-lyon.fr}\\
\LHead{Mathieu Nespoulous, Christophe Perge, Nicolas Taberlet, Thomas Gibaud,
Thibaut Divoux, Sébastien Manneville}

\LHead{\raisebox{-0.3em}{\includegraphics[height=\baselineskip]{CNRSfilaire-Q}\qquad\includegraphics[height=\baselineskip]{logo_UCBL}\qquad}\textsc{Laboratoire de Physique, Ecole Normale Supérieure de Lyon}\raisebox{-0.3em}{\qquad\includegraphics[height=\baselineskip]{logo_ens-lyon}}}

>>>>

\usepackage{hyperref}
\hypersetup{%
	pdftitle={Wrinkling and nested buckling in a confined protein gel},%the title
	pdfauthor={Mathieu Leocmach},%your name
}

@@

% This gives good title positioning for a portrait poster.
% Watch out for hyphenation in titles - LaTeX will do it
% but it looks awful.
\begin{textblock}{15}(0,0)
\centering
\Title{
Wrinkling of a confined porous layer
}

\smallskip
\LHead{Mathieu Leocmach, Mathieu Nespoulous, Thomas Gibaud, Sébastien Manneville
}\hfill\texttt{\color{Accent1}mathieu.leocmach@ens-lyon.fr}\\

\LHead{\textsc{Laboratoire de Physique, Ecole Normale Supérieure de Lyon}\hfill\raisebox{-1.5\baselineskip}{\includegraphics[height=2\baselineskip,clip=true, trim=0 10mm 0 0]{NEW-Logo-ERC-OUTLINE}\qquad\includegraphics[height=2\baselineskip]{CNRSfilaire-Q}\qquad\includegraphics[height=2\baselineskip]{logo_ens-lyon}}}
